### 2017-01-29 Radio/VLA_OH/VLA_2.tex
fix typo

\noindent The steep dependence between OH and FIR luminosities ($L_{\rm OH}^2\propto L_{\rm FIR}^2$; \Fig{model}a)
found in local OH ``megamasers'' (OHMs;  see \citealt[]{Lo05a} for a review) and
the ubiquity of strong IR-emitting galaxies found at high $z$ suggest that
the number density of OHM may improve current constraints on
the cosmic merger history \citep[hereafter DG02]{Darling02b_LF}. % but that's assuming IR-luminous must be driven by mergers....
Existing models predict that detections of
OHMs out to at least $z$\ssim3 are possible with current facilities (e.g. the GBT; \Fig{model}b).
Yet, despite several attempts,
the most distant OHM known-to-date was discovered over two decades ago, at $z$\eq0.265 \citep{Baan92a}.
The null detection in a $z$\ssim4 extremely IR-bright galaxy (\LIR$>10^{14}$\Lsun; \citealt{Ivison06a}) and
the remarkably low detection rate (7\%) from a sample of $>$120 IR-luminous galaxies
at $z$\,$\lesssim$\,1.5 ($L_{\rm IR}>10^{11}$\Lsun; \Fig{model}b; \citealt{Willett12a})
suggest a potential redshift evolution in the \LOH-\LFIR relation.
Detecting OHM beyond $z$\eq0.265 is therefore needed to enable a better understanding of the
OHM trigger mechanism, which may differ at earlier epochs due to different physical conditions of galaxies,
and to improve existing predictions to plan for future OHM surveys with upcoming facilities
\citep[e.g., FAST, APERTIF/WSRT, ASKAP;][]{Zhang14b}.
Here we propose to observe OH 1667 MHz line emission in the
gravitationally-lensed starbursting galaxy merger
RXJ1131 at $z$\eq0.65 (\Fig{hst}) using the VLA's B-array configuration.

>>>>

\noindent The steep dependence between OH and FIR luminosities ($L_{\rm OH}\propto L_{\rm FIR}^2$; \Fig{model}a)
found in local OH ``megamasers'' (OHMs;  see \citealt[]{Lo05a} for a review) and
the ubiquity of strong IR-emitting galaxies found at high $z$ suggest that
the number density of OHM may improve current constraints on
the cosmic merger history \citep[hereafter DG02]{Darling02b_LF}. % but that's assuming IR-luminous must be driven by mergers....
Existing models predict that detections of
OHMs out to at least $z$\ssim3 are possible with current facilities (e.g. the GBT; \Fig{model}b).
Yet, despite several attempts,
the most distant OHM known-to-date was discovered over two decades ago, at $z$\eq0.265 \citep{Baan92a}.
The null detection in a $z$\ssim4 extremely IR-bright galaxy (\LIR$>10^{14}$\Lsun; \citealt{Ivison06a}) and
the remarkably low detection rate (7\%) from a sample of $>$120 IR-luminous galaxies
at $z$\,$\lesssim$\,1.5 ($L_{\rm IR}>10^{11}$\Lsun; \Fig{model}b; \citealt{Willett12a})
suggest a potential redshift evolution in the \LOH-\LFIR relation.
Detecting OHM beyond $z$\eq0.265 is therefore needed to enable a better understanding of the
OHM trigger mechanism, which may differ at earlier epochs due to different physical conditions of galaxies,
and to improve existing predictions to plan for future OHM surveys with upcoming facilities
\citep[e.g., FAST, APERTIF/WSRT, ASKAP;][]{Zhang14b}.
Here we propose to observe OH 1667 MHz line emission in the
gravitationally-lensed starbursting galaxy merger
RXJ1131 at $z$\eq0.65 (\Fig{hst}) using the VLA's B-array configuration.
